---
title: "KCCA_integration"
author: "Ray Su"
date: "11/8/2020"
output:
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
library("tidyverse")
library("DT")
```

## Data Source


```{r data import}
Survival_status <- read.csv(file = "clinical_11082020.csv",stringsAsFactors = F)
colnames(Survival_status) <- c("SubjectID","DaysToDeath","SurvivalStatus")
datatable(Survival_status)
```

```{r,echo=FALSE,message=F}
b.outcome <- table(Survival_status$SurvivalStatus)
b.outcome[2]
```

## Data Summary

* Total Sample size: `r length(unique(Survival_status$SubjectID))`.
* `r b.outcome[2]` case samples.

# Method

## Image to matrix


## Omics data preprocess

### 

1. mRNA_selected.csv: normalized mRNA expression for selected genes and patients
2. methyl_selected.csv: beta values (extent of methylation) for selected genes and patients
3. mRNA_PCA.csv and methyl_selected.csv: top 10 PC by PCA. Values are first centered+scaled and then analyzed by PCA.
4. selected patients: patients with both imaging data (Udana's list) and with mRNA/methylation datasets (freshly downloaded from TCGA)
5. selected_genes: genes that are biologically important (Amin's list) and with non-NA values for all patients in the mRNA/methylation datasets.

* Based on the this [review](https://go.nature.com/2U5Dicc), we hypothesise that the top  mitochondrial-coding genes may capture the essence of the transcriptomic and methylatio status data, and as such, may constitute a more resolved feature-base.
* Human mitochondrial protein genes  were  collected from using Web Service Client as described here [link](https://bit.ly/3eDQsqA) or by manual download here [link](https://bit.ly/3laNhc6)
* The official/final of gene panels for downstream PCA  will applied to the subset of the mRNA and Methylation gene data that belong to the above-mentioned panel.


The updated date: 
*releaseDate: "2016-01-28";
*cohorts: 'GBM';

```{r}
mythyl <- read.csv(file = "../omics_preprocessing/methyl_selected.csv")
mRNA <- read.csv(file = "../omics_preprocessing/mRNA_selected.csv")
```



